A Beginners Guide to Perfomance Factors of Machine Learning Learning Applications with Focus on Neural Nets

### 2017-12-20 paper.tex
changes to Introduction containing the structure of the paper with the division into small and large scale applications

\IEEEpeerreviewmaketitle
\section{Introduction}
% no \IEEEPARstart
Machine Learning seems to be everywhere around us. With the success of Deep , Convolutional, Deep Belief, and other Neural Net specifications in the recent years because of the increasing capabilities of modern hardware, this trend continues to be more and more influencing on everyday application, may it be from music recommendation to personalized advertisement directly addressed to the consumer. But also in modern automation and research machine learning becomes a greater field managing to find more efficient ways to achieve better results in many expertise. We want to have a look at the most performance influencing factors of theses networks while designing and implementing them for specific applications for both small and large scale.

>>>>

\IEEEpeerreviewmaketitle
\section{Introduction}
Machine Learning seems to be everywhere around us. With the recent success of Deep, Convolutional and other Neural Networks, these kind of Machine Learning tools experience a kind of renaissance and usage in applications from industrial to service oriented. But also in modern automation and research machine learning becomes a greater field managing to find more efficient ways to achieve better results in many expertise. We want to have a look at the most performance influencing factors of theses networks while designing and implementing them for specific applications for both small and large scale. At first we attend the choice of neural network and the impact of this decision. Afterwards we chose to have a look, on one hand, at small scale neural networks running on a single machine without large data sets and a low query frequency after the initial training, and at the other hand, large scale neural networks operating with more layers and nodes, large data sets and distributed system to handle the computational power required by the neural network training algorithms to be completed in reasonable time.
